

\renewcommand{\abstractname}{Preface}
\renewcommand{\abstractnamefont}{\Huge\textbf}
\renewcommand{\abstracttextfont}{\normalsize}
\begin{abstract}
	
Traditional certificates with perforated edges have been the essence of earning an award. They play a role in acknowledging the person of the achievements earned. They serve an authentic message from the issuer about accomplishment to anyone who lay eyes on it.\\

Traditional certificates come with an incurred burden when the number of people getting certified grows. The generation of handmade or paper-based certificates takes from a week to a month. The details are can be erroneous as they are written by hand, re-issuing of such increase costs and time. Authentication and maintenance of the database for numerous certificates becomes a frantic work The cost and usage of paper also make traditional certificates not to be preferred in the current $ 21^{st}$ century.\\

Digitized E-Certificates can be generated within minutes and sent to the receiver via an e-mail or by uploading it on the cloud. A large number of certificates can be generated with minimal errors, also the errors can be rectified instantaneously. No postal costs and no downtime for hand written content. The e-certificates can be employed with security features involving advanced cryptographic techniques such as steganography and secure hash functions.\\

The Q-CERGEN software is aimed to facilitate the generation of such authentic and foolproof e-certificates. User-friendly interface with secured accounts and can generate a minimum of 3 certificates per second.


\vspace{0.5cm}
\begin{flushright}\textbf{Keshav V Bharadwaj}\end{flushright}
\begin{flushright}\textbf{Shankar Anbalagan}\end{flushright}
\begin{flushright}\textbf{Sourav P Adi}\end{flushright}
\begin{flushright}\textbf{Vivek B A}\end{flushright}

\vfill
\end{abstract}



